WASP-4 is Accelerating Toward the Earth

### 2020-02-09 paper/ms.tex
minor

Most of these data are identical to the data presented by
\citetalias{bouma_wasp4b_2019}.  Twenty-two new times reported by
\citet{southworth_transit_2019} are included.  These transits were
observed from the 3.58m New Technology Telescope and the Danish 1.54m
telescope at La Silla, Chile, and the South African Astronomical
Observatory 1.0m telescope.  Additional timing measurements were also
reported recently by \citet{baluev_2019}, based on a homogeneous
analysis of archival ground-based observations.  We included twelve of
their ``high quality'' transit times from the TRAPPIST telescope (six
transits), El~Sauce (four transits), and \citet{petrucci_no_2013}.
For TRAPPIST and El~Sauce, we verified with the original observers
that the timestamps were amenable to the appropriate barycentric and
leap second corrections (M.~Gillon, P.~Evans, priv{.} comm{.}).  We
omitted the fourteen remaining 
ETD\footnote{\url{http://var2.astro.cz/ETD}} times from \citeauthor{baluev_2019} due to ambiguity in
whether leap-second corrections had been performed.  We did not
include in our analysis the four occultation times tabulated by
\citetalias{bouma_wasp4b_2019}, because of the large timing
uncertainties and negligible statistical power.

>>>>

Most of these data are identical to the data presented by
\citetalias{bouma_wasp4b_2019}.  Twenty-two new times reported by
\citet{southworth_transit_2019} are included.  These transits were
observed from the 3.58m New Technology Telescope and the Danish 1.54m
telescope at La Silla, Chile, and the South African Astronomical
Observatory 1.0m telescope.  Additional timing measurements were also
reported recently by \citet{baluev_2019}, based on a homogeneous
analysis of archival ground-based observations.  We included twelve of
their ``high quality'' transit times from the TRAPPIST telescope (six
transits), the El~Sauce 36$\,$cm (four transits), and
\citet{petrucci_no_2013}.  For TRAPPIST and El~Sauce, we verified with
the original observers that the timestamps were amenable to the
appropriate barycentric and leap second corrections (M.~Gillon,
P.~Evans, priv{.} comm{.}).  We omitted the fourteen remaining
ETD\footnote{\url{http://var2.astro.cz/ETD}} times from
\citeauthor{baluev_2019} due to ambiguity in whether leap-second
corrections had been performed.  We did not include in our analysis
the four occultation times tabulated by
\citetalias{bouma_wasp4b_2019}, because of the large timing
uncertainties and negligible statistical power.
